```{r}
#| echo: false
#| message: false
#| warning: false
#| label: r-init-time-calculations

library(gtsummary)
library(gt)
library(dplyr)
library(tidyr)
library(stringr)
library(ggrain)
library(ggsci)

scale_colour_group <- function(...) {
  scale_colour_manual(
    values = c(
      "Intervention" = ggsci::pal_lancet(palette = "lanonc", alpha = 1)(2)[2],
      "Placebo" = ggsci::pal_lancet(palette = "lanonc", alpha = 1)(2)[1]
    )
  )
}

scale_fill_group <- function(...) {
  scale_fill_manual(
    values = c(
      "Intervention" = ggsci::pal_lancet(palette = "lanonc", alpha = 1)(2)[2],
      "Placebo" = ggsci::pal_lancet(palette = "lanonc", alpha = 1)(2)[1]
    )
  )
}

add_gg_theme <- function(plt) {
  plt <- plt +
    scale_fill_group() +
    scale_colour_group() +
    ggplot2::theme_classic() + 
    ggplot2::theme(
          axis.title = element_text(size = 16),
          axis.text = element_text(size = 14),
          legend.title = element_text(size = 16),
          legend.text = element_text(size = 14),
      )

  return(plt)
}

# global theme for gtsummary
gtsummary::theme_gtsummary_journal(journal = "lancet")

df <- dat_clean

bm_unpaired_test <- function(data, variable, by, ...) {

  # ---------------
  # Brunner-Munzel Test for unpaired data
  # ---------------

  formula <- as.formula(paste(variable, " ~ client_group"))

  bm_intervention <- npar.t.test(
    data[[variable]] ~ data[[by]],
    data = data,
    conf.level = 0.95,
    alternative = "two.sided",
    nperm = 10000,
    rounds = 3,
    info = FALSE,
    plot.simci = FALSE
)

  df <- data.frame(
    Effect = c(bm_intervention$Analysis$Effect),
    p.hat = c(bm_intervention$Analysis$Estimator),
    Lower = c(bm_intervention$Analysis$Lower),
    Upper = c(bm_intervention$Analysis$Upper),
    t.value = c(bm_intervention$Analysis$T),
    p.value = c(bm_intervention$Analysis$p)
  )

  df <- df %>%
    dplyr::mutate(
      ci.value = glue::glue("{Lower}, {Upper}")
    ) %>%
    dplyr::select(c(p.value))

  return(df)
}
```

### Cumulative time from baseline to finish module

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: r-prepare-rainplot-time-to-post-module

# RAIN plot (descriptive)
tmp_tmp = dat_clean %>%
      select(client_id, treatment, timepoint, Zeit_seit_Beginn_Modul_1_in_Jahren) %>% filter(timepoint != "Baseline" & !client_id %in% c(253, 396))

# convert to days
tmp_tmp <- tmp_tmp %>%
  mutate(Zeit_seit_Beginn_Modul_1_in_Jahren = Zeit_seit_Beginn_Modul_1_in_Jahren* 365.25)

tmp_tmp <- tmp_tmp %>%
  group_by(client_id) %>%
  arrange(client_id, timepoint) %>%
  mutate(
    Zeit_seit_Ende_des_vorigen_Moduls = Zeit_seit_Beginn_Modul_1_in_Jahren -
      lag(Zeit_seit_Beginn_Modul_1_in_Jahren, default = 0)
  ) %>%
  ungroup()
    
# RAIN plot (descriptive)
plt <- ggplot(tmp_tmp, aes(fill = treatment, x = timepoint, y = Zeit_seit_Ende_des_vorigen_Moduls, color = treatment)
  ) +
  geom_rain(
    seed = 42,
    rain.side = 'r',
    #id.long.var = "IoD_reduced",
    point.args = list(
      alpha = 0.3,
      shape = 21
    ),
    point.args.pos = rlang::list2(
      position = position_jitter(
        width = 0.1,
        height = 0.1
      )
    ),
    boxplot.args = list(
      outlier.shape = NA,
      color = "black",
      alpha = .7
    ),
    boxplot.args.pos = list(
      position = ggpp::position_dodgenudge(
        x = .25,
        width = 0.2
      ), 
      width = 0.15
    ),
    violin.args = list(
      alpha = .2
    ),
    violin.args.pos = list(
      position = ggpp::position_dodgenudge(
        x = .4,
        width = 0
      ), 
      width = 1.2
    ),
  ) +
  scale_y_log10() +
  labs(
    y = "Time since end of previous module (days)",
    x = "Timepoint",
    color = "Treatment",
    fill = "Treatment"
  )

plt <- add_gg_theme(plt)

ggsave(
  here::here("_figures/fig-time-to-post-module-rainplot.png"),
  plot = plt,
  dpi = 300,
  width = 16,
  height = 8,
)

ggsave(
  here::here("_figures/fig-time-to-post-module-rainplot.pdf"),
  plot = plt,
  dpi = 300,
  width = 16,
  height = 8
)
```

![Rainplot for time to finish the module. The time to finish the module is defined as time from end of the previous module to the end of the respective module. Note, that the time to finish the module consists of the time of working on the content and time for filling in questionnaires and time needed to revise guided tasks (and an undefined error term for doing things not related to the WBI). The y-axis is shown on a logarithmic scale.](_figures/fig-time-to-post-module-rainplot.png){#fig-time-to-post-module-rainplot width=100%}

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: r-time-to-post-module-mmrm

library(mmrm)

formular <- as.formula(
  paste(
      "Zeit_seit_Beginn_Modul_1_in_Jahren ~ timepoint + treatment:timepoint + us(timepoint | client_id)"
  )
)

fit_time_post_module <- mmrm(
    formula = formular,
    data = tmp_tmp %>% filter(timepoint!="Baseline" & !client_id %in% c(253, 396) ) %>% #  & client_id 533 hat kein Modul abgeschlossen
        dplyr::mutate(treatment = relevel(treatment, ref="Placebo"))
)

r_norm <- resid(fit_time_post_module, type = "normalized")

# QQ-plot & histogram
qqnorm(r_norm); qqline(r_norm)
hist(r_norm, breaks = "FD")

formular <- as.formula(
  paste(
      "log(Zeit_seit_Beginn_Modul_1_in_Jahren) ~ timepoint + treatment:timepoint + us(timepoint | client_id)"
  )
)

fit_time_post_module_log <- mmrm(
    formula = formular,
    data = tmp_tmp %>% filter(timepoint!="Baseline" & !client_id %in% c(253, 396) ) %>% #  & client_id 533 hat kein Modul abgeschlossen
        dplyr::mutate(treatment = relevel(treatment, ref="Placebo"))
)

r_norm <- resid(fit_time_post_module_log, type = "normalized")

# QQ-plot & histogram
qqnorm(r_norm); qqline(r_norm)
hist(r_norm, breaks = "FD")

tmp_tmp <- tmp_tmp %>%
  group_by(client_id) %>%
  arrange(client_id, timepoint) %>%
  mutate(
    Zeit_seit_Ende_des_vorigen_Moduls = Zeit_seit_Beginn_Modul_1_in_Jahren -
      lag(Zeit_seit_Beginn_Modul_1_in_Jahren, default = 0)
  ) %>%
  ungroup()

formular <- as.formula(
  paste(
      "log(Zeit_seit_Ende_des_vorigen_Moduls) ~ timepoint + treatment:timepoint + us(timepoint | client_id)"
  )
)

fit_time_post_module_non_cum <- mmrm(
    formula = formular,
    data = tmp_tmp %>% filter(timepoint!="Baseline" & !client_id %in% c(253, 396) ) %>% #  & client_id 533 hat kein Modul abgeschlossen
        dplyr::mutate(treatment = relevel(treatment, ref="Placebo"))
)

r_norm <- resid(fit_time_post_module_non_cum, type = "normalized")

# QQ-plot & histogram
qqnorm(r_norm); qqline(r_norm)
hist(r_norm, breaks = "FD")

```

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: tbl-time-to-post-module-mmrm
#| tbl-cap: "Mixed model for repeated measures (MMRM) for time to finish the module. The time to finish the module is defined as time from end of the previous module to the end of the respective module. Note, that the time to finish the module consists of the time of working on the content and time for filling in questionnaires and time needed to revise guided tasks (and an undefined error term for doing things not related to the WBI)."

my_log_lm_tidy <- function(x, ...) {
  df_tidy <- broom::tidy(x, ...)
  
  # exponentiate coef and CI
  if (TRUE) {
    df_tidy <-
      df_tidy %>%
      mutate_at(vars(any_of(c("estimate", "conf.low", "conf.high"))), exp)
  }
  
  df_tidy
}

tbl <- fit_time_post_module_non_cum %>%
    tbl_regression(
      add_estimate_to_reference_rows = TRUE,
      intercept = TRUE,
      label = list(
        treatment = "Treatment",
        timepoint = "Timepoint",
        `Timepoint * treatment` = "Timepoint * treatment"
      ), 
      tidy_fun = my_log_lm_tidy,
      estimate_fun = purrr::partial(style_ratio, digits = 2)
    ) %>%
    modify_header(label ~ "**Variable**",
                  estimate ~ "**exp(β)**") %>%
    remove_abbreviation("CI = Confidence Interval") %>%
    modify_abbreviation("CI = Confidence Interval") %>%
    modify_abbreviation("StGB = German penalty law") %>%
    modify_column_alignment(columns = everything(), align = "left") %>%
    modify_table_styling(
        columns = c(estimate, conf.low, conf.high),
        rows = reference_row %in% TRUE,
        missing_symbol = "Ref."
    ) %>%
    bold_labels() %>%
    as_gt() %>%
    gt::tab_options(
      table.font.names = "Times New Roman",
          table.font.size = 10,
          quarto.use_bootstrap = FALSE,
          quarto.disable_processing = TRUE,
          data_row.padding = px(1),
          summary_row.padding = gt::px(1),
          grand_summary_row.padding = gt::px(1),
          #footnotes.padding = gt::px(2),
          #source_notes.padding = gt::px(2),
          row_group.padding = gt::px(1)
    ) %>%
  tab_style(style = cell_text(align = "left"), locations = cells_source_notes()) %>%
  tab_style(style = cell_text(align = "left"), locations = cells_footnotes())

# save tbl as image
gt::gtsave(tbl, file = file.path(here::here("_tables/tbl-time-to-post-module-mmrm.pdf")))
gt::gtsave(tbl, file = file.path(here::here("_tables/tbl-time-to-post-module-mmrm.docx")))
gt::gtsave(tbl, file = file.path(here::here("_tables/tbl-time-to-post-module-mmrm.png")))

tbl
```

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: r-init-marginal-means-time-to-post-module

library(emmeans)

# Estimated marginal means
emm <- emmeans(fit_time_post_module_non_cum, ~ treatment | timepoint,
               type = "response")
emm_df <- as.data.frame(emm)

plt <- ggplot(
    emm_df, 
    aes(
      x = timepoint,
      y = response, 
      color = treatment, 
      group = treatment
    )
  ) +
  geom_line() +
  geom_point(size = 3) +
  geom_ribbon(
    aes(
      ymin = lower.CL, 
      ymax = upper.CL
    ),
    alpha = 0.2
  ) +
  labs(
    y = "Estimated marginal mean time (95%-CI)",
    x = "Timepoint",
    color = "Treatment",
    fill = "Treatment"
  )

plt <- add_gg_theme(plt)

ggsave(
  here::here("_figures/fig-time-to-post-module-estimated-marginal-means.png"),
  plot = plt,
  dpi = 300,
  width = 16,
  height = 8
)

ggsave(
  here::here("_figures/fig-time-to-post-module-estimated-marginal-means.pdf"),
  plot = plt,
  dpi = 300,
  width = 16,
  height = 8
)
```

![Estimated marginal means of the MMRM for time to finish the module. The time to finish the module is defined as time from end of the previous module to the end of the respective module. Note, that the time to finish module consists of the time of working on the content and time for filling in questionnaires and time needed to revise guided tasks (and an undefined error term for doing things not related to the WBI).](_figures/fig-time-to-post-module-estimated-marginal-means.png){#fig-time-to-post-module-estimated-marginal-means width=100%}

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: tbl-time-to-post-module-pairwise-comparisons
#| tbl-cap: "Pairwise comparisons for time to finish the module defined as time from end of the previous module to the end of the respective module. Note, that this time consists of the time of working on the content and time for filling in questionnaires and time needed to revise guided tasks (and an undefined error term for doing things not related to the WBI)."

df_m1toEndModule <- tmp_tmp %>%
  mutate(timepoint = gsub(".*([0-9]+).*", "\\1", timepoint)) %>%
  pivot_wider(
    names_from = timepoint,
    values_from = Zeit_seit_Ende_des_vorigen_Moduls,
    names_prefix = "module_"
  )


tbl <- df_m1toEndModule %>%
  dplyr::select(-client_id, -Zeit_seit_Beginn_Modul_1_in_Jahren) %>%
  tbl_summary(
    by = treatment,
    statistic = all_continuous() ~ c(
            "{mean} ({sd})",
            "{median} ({p25}, {p75})",
            "{min}, {max}"
          ),
    label = list(
      module_1 = "Module 1 (advised: 28 days)",
      module_2 = "Module 2 (advised: 28 days)",
      module_3 = "Module 3 (advised: 28 days)",
      module_4 = "Module 4 (advised: 28 days)",
      module_5 = "Module 5 (advised: 28 days)",
      module_6 = "Module 6 (advised: 28 days)"
    ),
    type = list(
      module_1 = "continuous2",
      module_2 = "continuous2",
      module_3 = "continuous2",
      module_4 = "continuous2",
      module_5 = "continuous2",
      module_6 = "continuous2"
    ),
    missing_text = "Missing"
  ) %>%
  # brunner-munzel test
    add_stat(fns = everything() ~ bm_unpaired_test) %>%
    add_q(method = "holm") %>%
    modify_header(
      p.value = "**p**"
    ) %>%
    bold_labels() %>%
    # damit quarto citations im footer erkeent, dürfen keine footnotes vorhanden sein!
    remove_footnote_header(columns = "q.value") %>%
    # abbreviations
    modify_abbreviation("Q1 = 25th percentile, Q3 = 75th percentile, p~adj~ = Holm-Bonferroni adjusted p.") %>%
    as_gt() %>%
    gt::tab_options(
      table.font.names = "Times New Roman",
          table.font.size = 10,
          quarto.use_bootstrap = FALSE,
          quarto.disable_processing = TRUE,
          data_row.padding = px(1),
          summary_row.padding = gt::px(1),
          grand_summary_row.padding = gt::px(1),
          #footnotes.padding = gt::px(2),
          #source_notes.padding = gt::px(2),
          row_group.padding = gt::px(1)
    ) %>%
  tab_style(style = cell_text(align = "left"), locations = cells_source_notes()) %>%
  tab_style(style = cell_text(align = "left"), locations = cells_footnotes())

# save tbl as image
gt::gtsave(tbl, file = file.path(here::here("_tables/tbl-time-to-post-module-pairwise-comparisons.pdf")))
gt::gtsave(tbl, file = file.path(here::here("_tables/tbl-time-to-post-module-pairwise-comparisons.docx")))
gt::gtsave(tbl, file = file.path(here::here("_tables/tbl-time-to-post-module-pairwise-comparisons.png")))

tbl
```

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: r-init-time-working-on-module
dataDir  <- file.path(projectDir, "data") # added
inDir    <- file.path(dataDir,    "input/2024-11-22/mtDatabase_26112024_FINAL") # added

log2 <- readRDS(file.path(inDir, "client_clientinterventionprogressdetailed.rds")) %>% mutate(
  lesson_duration = (lession_finished - lession_started)) # seconds  # added

# log2 <- readRDS(here::here("_data/MBSB/data/input/2024-11-22/mtDatabase_26112024_FINAL/client_clientinterventionprogressdetailed.rds")) %>% mutate(
#  lesson_duration = (lession_finished - lession_started)) # seconds 

# Create complete grid of all combinations
complete_grid <- expand.grid(
  client_id = unique(log2$client_id),
  current_module_nr = unique(log2$current_module_nr),
  current_session_nr = unique(log2$current_session_nr)
) %>%
  as_tibble()

# Join with original data and calculate session durations
log2_complete <- complete_grid %>%
  left_join(
    log2,
    by = c("client_id", "current_module_nr", "current_session_nr")
  ) %>%
  group_by(client_id, current_module_nr, current_session_nr) %>%
  mutate(
    session_duration = ifelse(
      any(is.na(lesson_duration)),
      NA_real_,
      sum(lesson_duration, na.rm = TRUE)
    )
  ) %>%
  ungroup() %>%
  distinct(client_id, current_module_nr, current_session_nr, .keep_all = TRUE) %>%
  filter(current_module_nr != 0) %>%
  filter(current_session_nr != 0)

# Calculate total module duration
log2_summary <- log2_complete %>%
  group_by(client_id, current_module_nr) %>%
  summarise(
    total_module_duration = as.numeric(sum(session_duration, na.rm = TRUE) / 3600), .groups = 'drop'
  ) %>%
  mutate(
    total_module_duration = ifelse(
      total_module_duration == 0,
      NA_real_,
      total_module_duration

    )
  )

log2_summary <- log2_summary %>% 
  mutate(
    # total_module_duration = ifelse(
    #   total_module_duration == 0,
    #   NA_real_,
    #   total_module_duration
    # ),
    client_id = factor(client_id)
  ) %>%
  mutate(
    timepoint = case_when(
      current_module_nr == 0 ~ "Baseline",
      current_module_nr == 1 ~ "Module 1 (post)",
      current_module_nr == 2 ~ "Module 2 (post)",
      current_module_nr == 3 ~ "Module 3 (post)",
      current_module_nr == 4 ~ "Module 4 (post)",
      current_module_nr == 5 ~ "Module 5 (post)",
      current_module_nr == 6 ~ "Module 6 (post)"
    )
  )

log2_joined <- dat_clean %>%
  dplyr::select(client_id, treatment, timepoint, module_duration_days) %>%
  filter(!client_id %in% c(253, 396)) %>%
  filter(timepoint != "Baseline") %>%
  right_join(log2_summary, by = c("client_id", "timepoint")) %>%
  mutate(
    time_sum_duration_lections_hours = ifelse(
      is.na(module_duration_days),
      NA_real_,
      total_module_duration
    ),
    timepoint = factor(timepoint)
  ) %>%
  filter(!is.na(treatment)) %>%
  mutate(
    timepoint = case_when(
      current_module_nr == 0 ~ "Baseline",
      current_module_nr == 1 ~ "Module 1 (post)",
      current_module_nr == 2 ~ "Module 2 (post)",
      current_module_nr == 3 ~ "Module 3 (post)",
      current_module_nr == 4 ~ "Module 4 (post)",
      current_module_nr == 5 ~ "Module 5 (post)",
      current_module_nr == 6 ~ "Module 6 (post)"
    )
  )
```

### Time working on module

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: r-prepare-rainplot-time-working-on-module

# RAIN plot (descriptive)
plt <- ggplot(log2_joined, aes(fill = treatment, x = timepoint, y = time_sum_duration_lections_hours, color = treatment)
  ) +
  ggrain::geom_rain(
    seed = 42,
    rain.side = 'r',
    #id.long.var = "time_sum_duration_lections_hours",
    point.args = list(
      alpha = 0.3,
      shape = 21
    ),
    point.args.pos = rlang::list2(
      position = position_jitter(
        seed = 42,
        width = 0.1,
        height = 0.1
      )
    ),
    boxplot.args = list(
      outlier.shape = NA,
      color = "black",
      alpha = .7
    ),
    boxplot.args.pos = list(
      position = ggpp::position_dodgenudge(
        x = .25,
        width = 0.2
      ), 
      width = 0.15
    ),
    violin.args = list(
      alpha = .2
    ),
    violin.args.pos = list(
      position = ggpp::position_dodgenudge(
        x = .4,
        width = 0
      ), 
      width = 1.2
    ),
  ) +
  scale_y_log10() +
  labs(
    y = "Time working on content (hours)",
    x = "Timepoint",
    color = "Treatment",
    fill = "Treatment"
  )

plt <- add_gg_theme(plt)

ggsave(
  here::here("_figures/fig-time-working-on-module-rainplot.png"),
  plot = plt,
  dpi = 300,
  width = 16,
  height = 8,
)

ggsave(
  here::here("_figures/fig-time-working-on-module-rainplot.pdf"),
  plot = plt,
  dpi = 300,
  width = 16,
  height = 8
)
```

![Rainplot for time working on content by module. The time working on content is defined as the sum of the time from creating a data base entry for lection data (at first visit of the lection page) to the time last change of database entry for this lection data occured for each lection the participant worked on in one module. This time difference can be interpreted as a narrow estimator for the time needed to finish the content of a WBI without the time needed for filling in questionnaires, reviews of guided tasks, or waiting times. But it includes the time needed for first answer of a guided exercise and times, in which the participant not logged in or logged in but not worked on the lection. The y-axis is shown on a logarithmic scale.](_figures/fig-time-working-on-module-rainplot.png){#fig-time-working-on-module-rainplot width=100%}

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: r-time-working-on-module-mmrm

library(mmrm)

formular <- as.formula(
  paste(
      "time_sum_duration_lections_hours ~ timepoint + treatment:timepoint + us(timepoint | client_id)"
  )
)

fit_time_post_module <- mmrm(
    formula = formular,
    data = log2_joined %>% filter(timepoint!="Baseline" & !client_id %in% c(253, 396) ) %>% #  & client_id 533 hat kein Modul abgeschlossen
    dplyr::mutate(treatment = relevel(treatment, ref="Placebo")) %>% mutate(timepoint = factor(timepoint))
)
r_norm <- resid(fit_time_post_module, type = "normalized")
# QQ-plot & histogram
# qqnorm(r_norm); qqline(r_norm)
# hist(r_norm, breaks = "FD")

# log transformed:
formular <- as.formula(
  paste(
      "log(time_sum_duration_lections_hours) ~ timepoint + treatment:timepoint + us(timepoint | client_id)"
  )
)

fit_time_post_module_log <- mmrm(
    formula = formular,
    data = log2_joined %>% filter(timepoint!="Baseline" & !client_id %in% c(253, 396) ) %>% #  & client_id 533 hat kein Modul abgeschlossen
    dplyr::mutate(treatment = relevel(treatment, ref="Placebo")) %>% mutate(timepoint = factor(timepoint))
)
r_norm <- resid(fit_time_post_module_log, type = "normalized")
# QQ-plot & histogram
# qqnorm(r_norm); qqline(r_norm) # looks good
# hist(r_norm, breaks = "FD")
```

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: tbl-time-working-on-module-mmrm
#| tbl-cap: "Mixed model for repeated measures (MMRM) for time working on content of one module of the WBI. The time working on content is defined as the sum of the time from creating a data base entry for lection data (at first visit of the lection page) to the time last change of database entry for this lection data occured for each lection the participant worked on in one module. This time difference can be interpreted as a narrow estimator for the time needed to finish the content of a WBI without the time needed for filling in questionnaires, reviews of guided tasks, or waiting times. But it includes the time needed for first answer of a guided exercise and times, in which the participant not logged in or logged in but not worked on the lection."

tbl <- fit_time_post_module_log %>%
    tbl_regression(
      add_estimate_to_reference_rows = TRUE,
      intercept = TRUE,
      label = list(
        treatment = "Treatment",
        timepoint = "Timepoint",
        `Timepoint * treatment` = "Timepoint * treatment", 
      tidy_fun = my_log_lm_tidy,
      estimate_fun = purrr::partial(style_ratio, digits = 2)
      )
    ) %>%
    modify_header(label ~ "**Variable**",
                  estimate ~ "**exp(β)**") %>%
    remove_abbreviation("CI = Confidence Interval") %>%
    modify_abbreviation("CI = Confidence Interval, StGB = German penalty law.") %>%
    modify_column_alignment(columns = everything(), align = "left") %>%
    modify_table_styling(
        columns = c(estimate, conf.low, conf.high),
        rows = reference_row %in% TRUE,
        missing_symbol = "Ref."
    ) %>%
    bold_labels() %>%
    as_gt() %>%
    gt::tab_options(
      table.font.names = "Times New Roman",
          table.font.size = 10,
          quarto.use_bootstrap = FALSE,
          quarto.disable_processing = TRUE,
          data_row.padding = px(1),
          summary_row.padding = gt::px(1),
          grand_summary_row.padding = gt::px(1),
          #footnotes.padding = gt::px(2),
          #source_notes.padding = gt::px(2),
          row_group.padding = gt::px(1)
    ) %>%
  tab_style(style = cell_text(align = "left"), locations = cells_source_notes()) %>%
  tab_style(style = cell_text(align = "left"), locations = cells_footnotes())

# save tbl as image
gt::gtsave(tbl, file = file.path(here::here("_tables/tbl-time-working-on-module-mmrm.pdf")))
gt::gtsave(tbl, file = file.path(here::here("_tables/tbl-time-working-on-module-mmrm.docx")))
gt::gtsave(tbl, file = file.path(here::here("_tables/tbl-time-working-on-module-mmrm.png")))

tbl
```

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: r-init-marginal-means-time-working-on-module

library(emmeans)

# Estimated marginal means
emm <- emmeans(fit_time_post_module_log, ~ treatment | timepoint,
               type = "response")
emm_df <- as.data.frame(emm)

plt <- ggplot(
    emm_df, 
    aes(
      x = timepoint,
      y = response, 
      color = treatment, 
      group = treatment
    )
  ) +
  geom_line() +
  geom_point(size = 3) +
  geom_ribbon(
    aes(
      ymin = lower.CL, 
      ymax = upper.CL
    ),
    alpha = 0.2
  ) +
  labs(
    y = "Estimated marginal mean time (95%-CI)",
    x = "Timepoint",
    color = "Treatment",
    fill = "Treatment"
  )
  
plt <- add_gg_theme(plt)

ggsave(
  here::here("_figures/fig-time-working-on-module-estimated-marginal-means.png"),
  plot = plt,
  dpi = 300,
  width = 16,
  height = 8
)

ggsave(
  here::here("_figures/fig-time-working-on-module-estimated-marginal-means.pdf"),
  plot = plt,
  dpi = 300,
  width = 16,
  height = 8
)
```

![Estimated marginal means for for time working on content of one module of the WBI. The time working on content is defined as the sum of the time from creating a data base entry for lection data (at first visit of the lection page) to the time last change of database entry for this lection data occured for each lection the participant worked on in one module. This time difference can be interpreted as a narrow estimator for the time needed to finish the content of a WBI without the time needed for filling in questionnaires, reviews of guided tasks, or waiting times. But it includes the time needed for first answer of a guided exercise and times, in which the participant not logged in or logged in but not worked on the lection.](_figures/fig-time-working-on-module-estimated-marginal-means.png){#fig-time-working-on-module-estimated-marginal-means width=100%}

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: tbl-time-working-on-module
#| tbl-cap: "Pairwise comparisons for time working on content by module. The time working on content is defined as the sum of the time from creating a data base entry for lection data (at first visit of a lection page) to the time last change of database entry for this lection data occured for each lection the participant worked on in one module. This time difference can be interpreted as a narrow estimator for the time needed to finish the content of a WBI without the time needed for filling in questionnaires, reviews of guided tasks, or waiting times. But it includes the time needed for first answer of a guided exercise and times, in which the participant not logged in or logged in but not worked on the lection."

df_working_time <- log2_joined %>%
  mutate(timepoint = gsub(".*([0-9]+).*", "\\1", timepoint)) %>%
  pivot_wider(
    names_from = timepoint,
    values_from = time_sum_duration_lections_hours,
    names_prefix = "module_"
  ) %>%
  select(-module_duration_days, -current_module_nr, -total_module_duration)

df_wide <- df_working_time %>%
  group_by(client_id) %>%
  summarise(
    across(
      starts_with("module_"),
      ~ if (all(is.na(.x))) NA else first(na.omit(.x))
    ),
    treatment = first(treatment),
    .groups = "drop"
  )


tbl <- df_wide %>%
  dplyr::select(-client_id) %>%
  tbl_summary(
    by = treatment,
    statistic = all_continuous() ~ c(
            "{mean} ({sd})",
            "{median} ({p25}, {p75})",
            "{min}, {max}"
          ),
    label = list(
      module_1 = "Module 1 (pre-tests: about 4 hours)",
      module_2 = "Module 2 (pre-tests: about 4 hours)",
      module_3 = "Module 3 (pre-tests: about 4 hours)",
      module_4 = "Module 4 (pre-tests: about 4 hours)",
      module_5 = "Module 5 (pre-tests: about 4 hours)",
      module_6 = "Module 6 (pre-tests: about 4 hours)"
    ),
    type = list(
      module_1 = "continuous2",
      module_2 = "continuous2",
      module_3 = "continuous2",
      module_4 = "continuous2",
      module_5 = "continuous2",
      module_6 = "continuous2"
    ),
    missing_text = "Missing"
  ) %>%
  # brunner-munzel test
    add_stat(fns = everything() ~ bm_unpaired_test) %>%
    add_q(method = "holm") %>%
    modify_header(
      p.value = "**p**"
    ) %>%
    bold_labels() %>%
    # damit quarto citations im footer erkeent, dürfen keine footnotes vorhanden sein!
    remove_footnote_header(columns = "q.value") %>%
    # abbreviations
    modify_abbreviation("Q1 = 25th percentile, Q3 = 75th percentile, p~adj~ = Holm-Bonferroni adjusted p.") %>%
    as_gt() %>%
    gt::tab_options(
      table.font.names = "Times New Roman",
          table.font.size = 10,
          quarto.use_bootstrap = FALSE,
          quarto.disable_processing = TRUE,
          data_row.padding = px(1),
          summary_row.padding = gt::px(1),
          grand_summary_row.padding = gt::px(1),
          #footnotes.padding = gt::px(2),
          #source_notes.padding = gt::px(2),
          row_group.padding = gt::px(1)
    ) %>%
  tab_style(style = cell_text(align = "left"), locations = cells_source_notes()) %>%
  tab_style(style = cell_text(align = "left"), locations = cells_footnotes())

# save tbl as image
gt::gtsave(tbl, file = file.path(here::here("_tables/tbl-time-working-on-module-pairwise-comparisons.pdf")))
gt::gtsave(tbl, file = file.path(here::here("_tables/tbl-time-working-on-module-pairwise-comparisons.docx")))
gt::gtsave(tbl, file = file.path(here::here("_tables/tbl-time-working-on-module-pairwise-comparisons.png")))

tbl
```
