```{r}
#| echo: false
#| message: false
#| warning: false
#| label: r-init-time-calculations

library(gtsummary)
library(gt)
library(dplyr)
library(tidyr)
library(stringr)
library(ggrain)
library(ggsci)

scale_colour_group <- function(...) {
  scale_colour_manual(
    values = c(
      "Intervention" = ggsci::pal_lancet(palette = "lanonc", alpha = 1)(2)[2],
      "Placebo" = ggsci::pal_lancet(palette = "lanonc", alpha = 1)(2)[1]
    ),
    breaks = c("Intervention", "Placebo")
  )
}

scale_color_group <- function(...) {
  scale_color_manual(
    values = c(
      "Intervention" = ggsci::pal_lancet(palette = "lanonc", alpha = 1)(2)[2],
      "Placebo" = ggsci::pal_lancet(palette = "lanonc", alpha = 1)(2)[1]
    ),
    breaks = c("Intervention", "Placebo")
  )
}

scale_fill_group <- function(...) {
  scale_fill_manual(
    values = c(
      "Intervention" = ggsci::pal_lancet(palette = "lanonc", alpha = 1)(2)[2],
      "Placebo" = ggsci::pal_lancet(palette = "lanonc", alpha = 1)(2)[1]
    ),
    breaks = c("Intervention", "Placebo")
  )
}

add_gg_theme <- function(plt) {
  
  # Gemeinsame override.aes Definition
  legend_override <- list(
    shape = 22,
    size = 5,
    linetype = 0,
    linewidth = 0,
    alpha = 0.8,
    colour = "black"
  )
  
  plt <- plt +
    scale_fill_group() +
    scale_colour_group() +
    scale_color_group() +
    ggplot2::theme_classic() + 
    ggplot2::theme(
      axis.title = element_text(size = 16),
      axis.text = element_text(size = 14),
      legend.title = element_text(size = 16),
      legend.text = element_text(size = 14),
    ) +
    guides(
      color     = guide_legend(title = "Treatment", order = 1, override.aes = legend_override),
      colour    = guide_legend(title = "Treatment", order = 1, override.aes = legend_override),
      fill      = guide_legend(title = "Treatment", order = 1, override.aes = legend_override),
      shape     = guide_legend(title = "Treatment", order = 1, override.aes = legend_override),
      linetype  = guide_legend(title = "Treatment", order = 1, override.aes = legend_override),
      size      = guide_legend(title = "Treatment", order = 1, override.aes = legend_override),
      alpha     = guide_legend(title = "Treatment", order = 1, override.aes = legend_override),
      linewidth = guide_legend(title = "Treatment", order = 1, override.aes = legend_override)
    )

  return(plt)
}

# global theme for gtsummary
gtsummary::theme_gtsummary_journal(journal = "lancet")

df <- dat_clean

bm_unpaired_test <- function(data, variable, by, ...) {

  # ---------------
  # Brunner-Munzel Test for unpaired data
  # ---------------

  formula <- as.formula(paste(variable, " ~ client_group"))

  bm_intervention <- npar.t.test(
    data[[variable]] ~ data[[by]],
    data = data,
    conf.level = 0.95,
    alternative = "two.sided",
    nperm = 10000,
    rounds = 3,
    info = FALSE,
    plot.simci = FALSE
)

  df <- data.frame(
    Effect = c(bm_intervention$Analysis$Effect),
    p.hat = c(bm_intervention$Analysis$Estimator),
    Lower = c(bm_intervention$Analysis$Lower),
    Upper = c(bm_intervention$Analysis$Upper),
    t.value = c(bm_intervention$Analysis$T),
    p.value = c(bm_intervention$Analysis$p)
  )

  df <- df %>%
    dplyr::mutate(
      ci.value = glue::glue("{Lower}, {Upper}")
    ) %>%
    dplyr::select(c(p.value))

  return(df)
}
```

### Time to finish module

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: r-prepare-rainplot-time-to-post-module

library(stringr)

# RAIN plot (descriptive)
tmp_tmp <- dat_clean %>%
  mutate(
    timepoint = stringr::str_remove(as.character(timepoint), " [(]post[)]"),
    timepoint = factor(timepoint)
  ) %>%
  select(client_id, treatment, timepoint, Zeit_seit_Beginn_Modul_1_in_Jahren) %>%
  filter(timepoint != "Baseline", !client_id %in% c(253, 396))

# convert to days
tmp_tmp <- tmp_tmp %>%
  mutate(Zeit_seit_Beginn_Modul_1_in_Jahren = Zeit_seit_Beginn_Modul_1_in_Jahren* 365.25)

tmp_tmp <- tmp_tmp %>%
  group_by(client_id) %>%
  arrange(client_id, timepoint) %>%
  mutate(
    Zeit_seit_Ende_des_vorigen_Moduls = Zeit_seit_Beginn_Modul_1_in_Jahren -
      lag(Zeit_seit_Beginn_Modul_1_in_Jahren, default = 0)
  ) %>%
  ungroup()
    
# RAIN plot (descriptive)
plt <- ggplot(tmp_tmp, aes(fill = treatment, x = timepoint, y = Zeit_seit_Ende_des_vorigen_Moduls, color = treatment)
  ) +
  geom_rain(
    seed = 42,
    rain.side = 'r',
    #id.long.var = "IoD_reduced",
    point.args = list(
      alpha = 0.3,
      shape = 21
    ),
    point.args.pos = rlang::list2(
      position = position_jitter(
        width = 0.1,
        height = 0.1
      )
    ),
    boxplot.args = list(
      outlier.shape = NA,
      color = "black",
      alpha = .7
    ),
    boxplot.args.pos = list(
      position = ggpp::position_dodgenudge(
        x = .25,
        width = 0.2
      ), 
      width = 0.15
    ),
    violin.args = list(
      alpha = .2
    ),
    violin.args.pos = list(
      position = ggpp::position_dodgenudge(
        x = .4,
        width = 0
      ), 
      width = 1.2
    ),
  ) +
  scale_y_log10() +
  labs(
    y = "Time to finish module (days)",
    x = "Timepoint",
    color = "Treatment",
    fill = "Treatment"
  )

plt <- add_gg_theme(plt)

ggsave(
  here::here("_figures/fig-time-to-finish-module-rainplot.png"),
  plot = plt,
  dpi = 300,
  width = 16,
  height = 8,
)

ggsave(
  here::here("_figures/fig-time-to-finish-module-rainplot.pdf"),
  plot = plt,
  dpi = 300,
  width = 16,
  height = 8
)
```

![Distribution of time to finish module for the intervention and placebo arms. Red denotes the intervention arm and blue denotes the placebo arm. Shown are log-transformed scores for each module. For each module, violin plots illustrate the score distributions, overlaid with boxplots indicating the median and interquartile range, and jittered points representing individual participants. The time to finish the module is defined as time from end of the previous module to the end of the respective module. Note, that the time to finish the module consists of the time of working on the content and time for filling in questionnaires and time needed to revise guided tasks (and an undefined error term for doing things not related to the WBI).](_figures/fig-time-to-finish-module-rainplot.png){#fig-time-to-finish-module-rainplot width=100%}

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: r-time-to-finish-module-diagnostic-plots

library(mmrm)

tmp_tmp <- tmp_tmp %>%
  group_by(client_id) %>%
  arrange(client_id, timepoint) %>%
  mutate(
    Zeit_seit_Ende_des_vorigen_Moduls = Zeit_seit_Beginn_Modul_1_in_Jahren -
      lag(Zeit_seit_Beginn_Modul_1_in_Jahren, default = 0)
  ) %>%
  ungroup()

formular <- as.formula(
  paste(
      "Zeit_seit_Ende_des_vorigen_Moduls ~ timepoint + treatment:timepoint + us(timepoint | client_id)"
  )
)

fit_time_post_module <- mmrm(
    formula = formular,
    data = tmp_tmp %>% filter(timepoint!="Baseline" & !client_id %in% c(253, 396) ) %>% #  & client_id 533 hat kein Modul abgeschlossen
        dplyr::mutate(treatment = relevel(treatment, ref="Placebo"))
)

formular <- as.formula(
  paste(
      "log(Zeit_seit_Ende_des_vorigen_Moduls) ~ timepoint + treatment:timepoint + us(timepoint | client_id)"
  )
)

fit_time_post_module_non_cum <- mmrm(
    formula = formular,
    data = tmp_tmp %>% filter(timepoint!="Baseline" & !client_id %in% c(253, 396) ) %>% #  & client_id 533 hat kein Modul abgeschlossen
        dplyr::mutate(treatment = relevel(treatment, ref="Placebo"))
)

library(ggplot2)
library(patchwork)

df1 <- data.frame(resid = resid(fit_time_post_module, type = "normalized"))
df2 <- data.frame(resid = resid(fit_time_post_module_non_cum, type = "normalized"))

p1 <- ggplot(df1, aes(sample = resid)) +
  stat_qq() +
  stat_qq_line()

p1 <- add_gg_theme(p1)

p2 <- ggplot(df1, aes(x = resid)) +
  geom_histogram(bins = 30)

p2 <- add_gg_theme(p2)

p3 <- ggplot(df2, aes(sample = resid)) +
  stat_qq() +
  stat_qq_line()

p3 <- add_gg_theme(p3)

p4 <- ggplot(df2, aes(x = resid)) +
  geom_histogram(bins = 30)

p4 <- add_gg_theme(p4)

plt <- (p1 / p2) | (p3 / p4)

name_png <- glue("_figures/fig-time-to-finish-module-diagnostic-plots.png")
name_pdf <- glue("_figures/fig-time-to-finish-module-diagnostic-plots.pdf")

ggsave(
    here::here(name_png),
    plot = plt,
    dpi = 300,
    width = 16,
    height = 16,
)

ggsave(
    here::here(name_pdf),
    plot = plt,
    dpi = 300,
    width = 16,
    height = 16
)
```
  

![Diagnostic plots for time to finish module. The plots on the left correspond to the model fitted with raw scores, the plots on the right correspond to the model fitted with log-transformed scores. The plots indicate violations of the normality assumption; therefore, the model was fitted with log-transformed scores.](_figures/fig-time-to-finish-module-diagnostic-plots.png){#fig-time-to-finish-module-diagnostic-plots}

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: tbl-time-to-finish-module-mmrm
#| tbl-cap: "Mixed model for repeated measures (MMRM) for time to finish the module. The time to finish the module is defined as time from end of the previous module to the end of the respective module. Note, that the time to finish the module consists of the time of working on the content and time for filling in questionnaires and time needed to revise guided tasks (and an undefined error term for doing things not related to the WBI). Note, that the model is fitted on log-transformed data."

my_log_lm_tidy <- function(x, ...) {
  df_tidy <- broom::tidy(x, ...)
  
  # exponentiate coef and CI
  if (TRUE) {
    df_tidy <-
      df_tidy %>%
      mutate_at(vars(any_of(c("estimate", "conf.low", "conf.high"))), exp)
  }
  
  df_tidy
}

tbl <- fit_time_post_module_non_cum %>%
    tbl_regression(
      add_estimate_to_reference_rows = TRUE,
      intercept = TRUE,
      label = list(
        treatment = "Treatment",
        timepoint = "Timepoint",
        `Timepoint * treatment` = "Timepoint * treatment"
      ), 
      tidy_fun = my_log_lm_tidy,
      estimate_fun = purrr::partial(style_ratio, digits = 2)
    ) %>%
    modify_header(label ~ "**Variable**",
                  p.value ~ "**p**",
                  estimate ~ "**Beta**") %>%
    remove_abbreviation("CI = Confidence Interval") %>%
    modify_abbreviation("CI = Confidence Interval") %>%
    modify_abbreviation("StGB = German penalty law") %>%
    modify_column_alignment(columns = everything(), align = "left") %>%
    modify_table_styling(
        columns = c(estimate, conf.low, conf.high),
        rows = reference_row %in% TRUE,
        missing_symbol = "Ref."
    ) %>%
    bold_labels()

tbl_a <- tbl %>%
    as_gt() %>%
    gt::tab_options(
      table.font.names = "Times New Roman",
          table.font.size = 10,
          quarto.use_bootstrap = FALSE,
          quarto.disable_processing = TRUE,
          data_row.padding = px(1),
          summary_row.padding = gt::px(1),
          grand_summary_row.padding = gt::px(1),
          row_group.padding = gt::px(1)
    ) %>%
  tab_style(style = cell_text(align = "left"), locations = cells_source_notes()) %>%
  tab_style(style = cell_text(align = "left"), locations = cells_footnotes())

# save tbl as image
gt::gtsave(tbl_a, file = file.path(here::here("_tables/tbl-time-to-finish-module-mmrm.pdf")))
gt::gtsave(tbl_a, file = file.path(here::here("_tables/tbl-time-to-finish-module-mmrm.docx")))
gt::gtsave(tbl_a, file = file.path(here::here("_tables/tbl-time-to-finish-module-mmrm.png")))

tbl <- tbl %>%
    as_kable_extra(
        booktabs = TRUE,
        linesep = ""
    ) %>%
    kable_styling(
        latex_options = c("scale_down", "hold_position"),
        full_width = TRUE,
        font_size = 8
    )

tbl
```

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: r-init-marginal-means-time-to-finish-module

library(emmeans)

# Estimated marginal means
emm <- emmeans(fit_time_post_module_non_cum, ~ treatment | timepoint,
               type = "response")
emm_df <- as.data.frame(emm)

plt <- ggplot(
    emm_df, 
    aes(
      x = timepoint,
      y = response, 
      color = treatment,
      fill = treatment,
      group = treatment
    )
  ) +
  geom_line() +
  geom_point(size = 3) +
  geom_ribbon(
    aes(
      ymin = lower.CL, 
      ymax = upper.CL
    ),
    alpha = 0.2
  ) +
  labs(
    y = "Estimated marginal mean time (95%-CI)",
    x = "Timepoint",
    color = "Treatment",
    fill = "Treatment"
  )

plt <- add_gg_theme(plt)

ggsave(
  here::here("_figures/fig-time-to-finish-module-estimated-marginal-means.png"),
  plot = plt,
  dpi = 300,
  width = 16,
  height = 8
)

ggsave(
  here::here("_figures/fig-time-to-finish-module-estimated-marginal-means.pdf"),
  plot = plt,
  dpi = 300,
  width = 16,
  height = 8
)
```

![Estimated marginal means of the MMRM for time to finish a module. The time to finish a module is defined as time from end of the previous module to the end of the respective module. Note, that the time to finish module consists of the time of working on the content and time for filling in questionnaires and time needed to revise guided tasks (and an undefined error term for doing things not related to the WBI).](_figures/fig-time-to-finish-module-estimated-marginal-means.png){#fig-time-to-finish-module-estimated-marginal-means width=100%}

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: tbl-time-to-finish-module-pairwise-comparisons
#| tbl-cap: "Results of the Brunner-Munzel tests for unpaired data for time to finish a module. Note, that this time consists of the time of working on the content and time for filling in questionnaires and time needed to revise guided tasks (and an undefined error term for doing things not related to the WBI)."

df_m1toEndModule <- tmp_tmp %>%
  mutate(timepoint = gsub(".*([0-9]+).*", "\\1", timepoint)) %>%
  pivot_wider(
    names_from = timepoint,
    values_from = Zeit_seit_Ende_des_vorigen_Moduls,
    names_prefix = "module_"
  )


tbl <- df_m1toEndModule %>%
  dplyr::select(-client_id, -Zeit_seit_Beginn_Modul_1_in_Jahren) %>%
  tbl_summary(
    by = treatment,
    statistic = all_continuous() ~ c(
            "{mean} ({sd})",
            "{median} ({p25}, {p75})",
            "{min}, {max}"
          ),
    label = list(
      module_1 = "Module 1 (advised: 28 days)",
      module_2 = "Module 2 (advised: 28 days)",
      module_3 = "Module 3 (advised: 28 days)",
      module_4 = "Module 4 (advised: 28 days)",
      module_5 = "Module 5 (advised: 28 days)",
      module_6 = "Module 6 (advised: 28 days)"
    ),
    type = list(
      module_1 = "continuous2",
      module_2 = "continuous2",
      module_3 = "continuous2",
      module_4 = "continuous2",
      module_5 = "continuous2",
      module_6 = "continuous2"
    ),
    missing_text = "Missing"
  ) %>%
  # brunner-munzel test
    add_stat(fns = everything() ~ bm_unpaired_test) %>%
    add_q(method = "holm") %>%
    modify_header(
      p.value = "**p**",
      q.value = "**q**"
    ) %>%
    bold_labels() %>%
    # damit quarto citations im footer erkeent, dürfen keine footnotes vorhanden sein!
    remove_footnote_header(columns = "q.value") %>%
    # abbreviations
    modify_abbreviation("Q1 = 25th percentile, Q3 = 75th percentile, SD = Standard deviation, q = Holm-Bonferroni adjusted p.")

tbl_a <- tbl %>%
    as_gt() %>%
    gt::tab_options(
      table.font.names = "Times New Roman",
          table.font.size = 10,
          quarto.use_bootstrap = FALSE,
          quarto.disable_processing = TRUE,
          data_row.padding = px(1),
          summary_row.padding = gt::px(1),
          grand_summary_row.padding = gt::px(1),
          row_group.padding = gt::px(1)
    ) %>%
  tab_style(style = cell_text(align = "left"), locations = cells_source_notes()) %>%
  tab_style(style = cell_text(align = "left"), locations = cells_footnotes())

# save tbl as image
gt::gtsave(tbl_a, file = file.path(here::here("_tables/tbl-time-to-finish-module-pairwise-comparisons.pdf")))
gt::gtsave(tbl_a, file = file.path(here::here("_tables/tbl-time-to-finish-module-pairwise-comparisons.docx")))
gt::gtsave(tbl_a, file = file.path(here::here("_tables/tbl-time-to-finish-module-pairwise-comparisons.png")))

tbl <- tbl %>%
    as_kable_extra(
        booktabs = TRUE,
        linesep = ""
    ) %>%
    kable_styling(
        latex_options = c("scale_down", "hold_position"),
        full_width = TRUE,
        font_size = 8
    )

tbl
```

### Time working on module

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: r-init-time-working-on-module
dataDir  <- file.path(projectDir, "data") # added
inDir    <- file.path(dataDir,    "input/2024-11-22/mtDatabase_26112024_FINAL") # added

log2 <- readRDS(file.path(inDir, "client_clientinterventionprogressdetailed.rds")) %>% mutate(
  lesson_duration = (lession_finished - lession_started)) # seconds  # added

# log2 <- readRDS(here::here("_data/MBSB/data/input/2024-11-22/mtDatabase_26112024_FINAL/client_clientinterventionprogressdetailed.rds")) %>% mutate(
#  lesson_duration = (lession_finished - lession_started)) # seconds 

# Create complete grid of all combinations
complete_grid <- expand.grid(
  client_id = unique(log2$client_id),
  current_module_nr = unique(log2$current_module_nr),
  current_session_nr = unique(log2$current_session_nr)
) %>%
  as_tibble()

# Join with original data and calculate session durations
log2_complete <- complete_grid %>%
  left_join(
    log2,
    by = c("client_id", "current_module_nr", "current_session_nr")
  ) %>%
  group_by(client_id, current_module_nr, current_session_nr) %>%
  mutate(
    session_duration = ifelse(
      any(is.na(lesson_duration)),
      NA_real_,
      sum(lesson_duration, na.rm = TRUE)
    )
  ) %>%
  ungroup() %>%
  distinct(client_id, current_module_nr, current_session_nr, .keep_all = TRUE) %>%
  filter(current_module_nr != 0) %>%
  filter(current_session_nr != 0)

# Calculate total module duration
log2_summary <- log2_complete %>%
  group_by(client_id, current_module_nr) %>%
  summarise(
    total_module_duration = as.numeric(sum(session_duration, na.rm = TRUE) / 3600), .groups = 'drop'
  ) %>%
  mutate(
    total_module_duration = ifelse(
      total_module_duration == 0,
      NA_real_,
      total_module_duration

    )
  )

log2_summary <- log2_summary %>% 
  mutate(client_id = factor(client_id)) %>%
  mutate(
    timepoint = case_when(
      current_module_nr == 0 ~ "Baseline",
      current_module_nr == 1 ~ "Module 1 (post)",
      current_module_nr == 2 ~ "Module 2 (post)",
      current_module_nr == 3 ~ "Module 3 (post)",
      current_module_nr == 4 ~ "Module 4 (post)",
      current_module_nr == 5 ~ "Module 5 (post)",
      current_module_nr == 6 ~ "Module 6 (post)"
    )
  )

log2_joined <- dat_clean %>%
  dplyr::select(client_id, treatment, timepoint, module_duration_days) %>%
  filter(!client_id %in% c(253, 396)) %>%
  filter(timepoint != "Baseline") %>%
  right_join(log2_summary, by = c("client_id", "timepoint")) %>%
  mutate(
    time_sum_duration_lections_hours = ifelse(
      is.na(module_duration_days),
      NA_real_,
      total_module_duration
    ),
    timepoint = factor(timepoint)
  ) %>%
  filter(!is.na(treatment)) %>%
  mutate(
    timepoint = case_when(
      current_module_nr == 0 ~ "Baseline",
      current_module_nr == 1 ~ "Module 1",
      current_module_nr == 2 ~ "Module 2",
      current_module_nr == 3 ~ "Module 3",
      current_module_nr == 4 ~ "Module 4",
      current_module_nr == 5 ~ "Module 5",
      current_module_nr == 6 ~ "Module 6"
    )
  )
```

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: r-prepare-rainplot-time-working-on-module

# RAIN plot (descriptive)
plt <- ggplot(log2_joined, aes(fill = treatment, x = timepoint, y = time_sum_duration_lections_hours, color = treatment)
  ) +
  ggrain::geom_rain(
    seed = 42,
    rain.side = 'r',
    #id.long.var = "time_sum_duration_lections_hours",
    point.args = list(
      alpha = 0.3,
      shape = 21
    ),
    point.args.pos = rlang::list2(
      position = position_jitter(
        seed = 42,
        width = 0.1,
        height = 0.1
      )
    ),
    boxplot.args = list(
      outlier.shape = NA,
      color = "black",
      alpha = .7
    ),
    boxplot.args.pos = list(
      position = ggpp::position_dodgenudge(
        x = .25,
        width = 0.2
      ), 
      width = 0.15
    ),
    violin.args = list(
      alpha = .2
    ),
    violin.args.pos = list(
      position = ggpp::position_dodgenudge(
        x = .4,
        width = 0
      ), 
      width = 1.2
    ),
  ) +
  scale_y_log10() +
  labs(
    y = "Time working on content (hours)",
    x = "Timepoint",
    color = "Treatment",
    fill = "Treatment"
  )

plt <- add_gg_theme(plt)

ggsave(
  here::here("_figures/fig-time-working-on-module-rainplot.png"),
  plot = plt,
  dpi = 300,
  width = 16,
  height = 8,
)

ggsave(
  here::here("_figures/fig-time-working-on-module-rainplot.pdf"),
  plot = plt,
  dpi = 300,
  width = 16,
  height = 8
)
```

![Distribution of time working on content for the intervention and placebo arms. Red denotes the intervention arm and blue denotes the placebo arm. Shown are log-transformed scores for each module. For each module, violin plots illustrate the score distributions, overlaid with boxplots indicating the median and interquartile range, and jittered points representing individual participants. The time working on content is defined as the sum of the time from creating a data base entry for lection data (at first visit of the lection page) to the time last change of database entry for this lection data occured for each lection the participant worked on in one module. This time difference can be interpreted as a narrow estimator for the time needed to finish the content of a WBI without the time needed for filling in questionnaires, reviews of guided tasks, or waiting times. But it includes the time needed for first answer of a guided exercise and times, in which the participant not logged in or logged in but not worked on the lection.](_figures/fig-time-working-on-module-rainplot.png){#fig-time-working-on-module-rainplot width=100%}

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: r-time-working-on-module-diagnostic-plots

library(mmrm)

formular <- as.formula(
  paste(
      "time_sum_duration_lections_hours ~ timepoint + treatment:timepoint + us(timepoint | client_id)"
  )
)

fit_time_post_module <- mmrm(
    formula = formular,
    data = log2_joined %>% filter(timepoint!="Baseline" & !client_id %in% c(253, 396) ) %>% #  & client_id 533 hat kein Modul abgeschlossen
    dplyr::mutate(treatment = relevel(treatment, ref="Placebo")) %>% mutate(timepoint = factor(timepoint))
)
r_norm <- resid(fit_time_post_module, type = "normalized")

# log transformed:
formular <- as.formula(
  paste(
      "log(time_sum_duration_lections_hours) ~ timepoint + treatment:timepoint + us(timepoint | client_id)"
  )
)

fit_time_post_module_log <- mmrm(
    formula = formular,
    data = log2_joined %>% filter(timepoint!="Baseline" & !client_id %in% c(253, 396) ) %>% #  & client_id 533 hat kein Modul abgeschlossen
    dplyr::mutate(treatment = relevel(treatment, ref="Placebo")) %>% mutate(timepoint = factor(timepoint))
)
r_norm <- resid(fit_time_post_module_log, type = "normalized")

library(ggplot2)
library(patchwork)

df1 <- data.frame(resid = resid(fit_time_post_module, type = "normalized"))
df2 <- data.frame(resid = resid(fit_time_post_module_non_cum, type = "normalized"))

p1 <- ggplot(df1, aes(sample = resid)) +
  stat_qq() +
  stat_qq_line()

p1 <- add_gg_theme(p1)

p2 <- ggplot(df1, aes(x = resid)) +
  geom_histogram(bins = 30)

p2 <- add_gg_theme(p2)

p3 <- ggplot(df2, aes(sample = resid)) +
  stat_qq() +
  stat_qq_line()

p3 <- add_gg_theme(p3)

p4 <- ggplot(df2, aes(x = resid)) +
  geom_histogram(bins = 30)

p4 <- add_gg_theme(p4)

plt <- (p1 / p2) | (p3 / p4)

name_png <- glue("_figures/fig-time-working-on-module-diagnostic-plots.png")
name_pdf <- glue("_figures/fig-time-working-on-module-diagnostic-plots.pdf")

ggsave(
    here::here(name_png),
    plot = plt,
    dpi = 300,
    width = 16,
    height = 16,
)

ggsave(
    here::here(name_pdf),
    plot = plt,
    dpi = 300,
    width = 16,
    height = 16
)
```
  

![Diagnostic plots for time working on content module. The plots on the left correspond to the model fitted with raw scores, the plots on the right correspond to the model fitted with log-transformed scores. The plots indicate violations of the normality assumption; therefore, the model was fitted with log-transformed scores.](_figures/fig-time-working-on-module-diagnostic-plots.png){#fig-time-working-on-module-diagnostic-plots}

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: tbl-time-working-on-module-mmrm
#| tbl-cap: "Mixed model for repeated measures (MMRM) for time working on content of one module of the WBI. The time working on content is defined as the sum of the time from creating a data base entry for lection data (at first visit of the lection page) to the time last change of database entry for this lection data occured for each lection the participant worked on in one module. This time difference can be interpreted as a narrow estimator for the time needed to finish the content of a WBI without the time needed for filling in questionnaires, reviews of guided tasks, or waiting times. But it includes the time needed for first answer of a guided exercise and times, in which the participant not logged in or logged in but not worked on the lection."

tbl <- fit_time_post_module_log %>%
    tbl_regression(
      add_estimate_to_reference_rows = TRUE,
      intercept = TRUE,
      label = list(
        treatment = "Treatment",
        timepoint = "Timepoint",
        `Timepoint * treatment` = "Timepoint * treatment", 
      tidy_fun = my_log_lm_tidy,
      estimate_fun = purrr::partial(style_ratio, digits = 2)
      )
    ) %>%
    modify_header(label ~ "**Variable**",
                  p.value ~ "**p**",
                  estimate ~ "**Beta**") %>%
    remove_abbreviation("CI = Confidence Interval") %>%
    modify_abbreviation("CI = Confidence Interval, StGB = German penalty law.") %>%
    modify_column_alignment(columns = everything(), align = "left") %>%
    modify_table_styling(
        columns = c(estimate, conf.low, conf.high),
        rows = reference_row %in% TRUE,
        missing_symbol = "Ref."
    ) %>%
    bold_labels()

tbl_a <- tbl %>%
    as_gt() %>%
    gt::tab_options(
      table.font.names = "Times New Roman",
          table.font.size = 10,
          quarto.use_bootstrap = FALSE,
          quarto.disable_processing = TRUE,
          data_row.padding = px(1),
          summary_row.padding = gt::px(1),
          grand_summary_row.padding = gt::px(1),
          row_group.padding = gt::px(1)
    ) %>%
  tab_style(style = cell_text(align = "left"), locations = cells_source_notes()) %>%
  tab_style(style = cell_text(align = "left"), locations = cells_footnotes())

# save tbl as image
gt::gtsave(tbl_a, file = file.path(here::here("_tables/tbl-time-working-on-module-mmrm.pdf")))
gt::gtsave(tbl_a, file = file.path(here::here("_tables/tbl-time-working-on-module-mmrm.docx")))
gt::gtsave(tbl_a, file = file.path(here::here("_tables/tbl-time-working-on-module-mmrm.png")))

tbl <- tbl %>%
    as_kable_extra(
        booktabs = TRUE,
        linesep = ""
    ) %>%
    kable_styling(
        latex_options = c("scale_down", "hold_position"),
        full_width = TRUE,
        font_size = 8
    )

tbl
```

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: r-init-marginal-means-time-working-on-module

library(emmeans)

# Estimated marginal means
emm <- emmeans(fit_time_post_module_log, ~ treatment | timepoint,
               type = "response")
emm_df <- as.data.frame(emm)

plt <- ggplot(
    emm_df, 
    aes(
      x = timepoint,
      y = response, 
      color = treatment, 
      fill = treatment,
      group = treatment
    )
  ) +
  geom_line() +
  geom_point(size = 3) +
  geom_ribbon(
    aes(
      ymin = lower.CL, 
      ymax = upper.CL
    ),
    alpha = 0.2
  ) +
  labs(
    y = "Estimated marginal mean time (95%-CI)",
    x = "Timepoint",
    color = "Treatment",
    fill = "Treatment"
  )
  
plt <- add_gg_theme(plt)

ggsave(
  here::here("_figures/fig-time-working-on-module-estimated-marginal-means.png"),
  plot = plt,
  dpi = 300,
  width = 16,
  height = 8
)

ggsave(
  here::here("_figures/fig-time-working-on-module-estimated-marginal-means.pdf"),
  plot = plt,
  dpi = 300,
  width = 16,
  height = 8
)
```

![Estimated marginal means for for time working on content of one module of the WBI. The time working on content is defined as the sum of the time from creating a data base entry for lection data (at first visit of the lection page) to the time last change of database entry for this lection data occured for each lection the participant worked on in one module. This time difference can be interpreted as a narrow estimator for the time needed to finish the content of a WBI without the time needed for filling in questionnaires, reviews of guided tasks, or waiting times. But it includes the time needed for first answer of a guided exercise and times, in which the participant not logged in or logged in but not worked on the lection.](_figures/fig-time-working-on-module-estimated-marginal-means.png){#fig-time-working-on-module-estimated-marginal-means width=100%}

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: tbl-time-working-on-module
#| tbl-cap: "Results of the Brunner-Munzel tests for unpaired data for time working on content by module. The time working on content is defined as the sum of the time from creating a data base entry for lection data (at first visit of a lection page) to the time last change of database entry for this lection data occured for each lection the participant worked on in one module. This time difference can be interpreted as a narrow estimator for the time needed to finish the content of a WBI without the time needed for filling in questionnaires, reviews of guided tasks, or waiting times. But it includes the time needed for first answer of a guided exercise and times, in which the participant not logged in or logged in but not worked on the lection."

df_working_time <- log2_joined %>%
  mutate(timepoint = gsub(".*([0-9]+).*", "\\1", timepoint)) %>%
  pivot_wider(
    names_from = timepoint,
    values_from = time_sum_duration_lections_hours,
    names_prefix = "module_"
  ) %>%
  select(-module_duration_days, -current_module_nr, -total_module_duration)

df_wide <- df_working_time %>%
  group_by(client_id) %>%
  summarise(
    across(
      starts_with("module_"),
      ~ if (all(is.na(.x))) NA else first(na.omit(.x))
    ),
    treatment = first(treatment),
    .groups = "drop"
  )


tbl <- df_wide %>%
  dplyr::select(-client_id) %>%
  tbl_summary(
    by = treatment,
    statistic = all_continuous() ~ c(
            "{mean} ({sd})",
            "{median} ({p25}, {p75})",
            "{min}, {max}"
          ),
    label = list(
      module_1 = "Module 1 (pre-tests: about 4 hours)",
      module_2 = "Module 2 (pre-tests: about 4 hours)",
      module_3 = "Module 3 (pre-tests: about 4 hours)",
      module_4 = "Module 4 (pre-tests: about 4 hours)",
      module_5 = "Module 5 (pre-tests: about 4 hours)",
      module_6 = "Module 6 (pre-tests: about 4 hours)"
    ),
    type = list(
      module_1 = "continuous2",
      module_2 = "continuous2",
      module_3 = "continuous2",
      module_4 = "continuous2",
      module_5 = "continuous2",
      module_6 = "continuous2"
    ),
    missing_text = "Missing"
  ) %>%
  # brunner-munzel test
    add_stat(fns = everything() ~ bm_unpaired_test) %>%
    add_q(method = "holm") %>%
    modify_header(
      p.value = "**p**",
      q.value = "**q**"
    ) %>%
    bold_labels() %>%
    # damit quarto citations im footer erkeent, dürfen keine footnotes vorhanden sein!
    remove_footnote_header(columns = "q.value") %>%
    # abbreviations
    modify_abbreviation("Q1 = 25th percentile, Q3 = 75th percentile, SD = Standard deviance, q = Holm-Bonferroni adjusted p.")

tbl_a <- tbl %>%
    as_gt() %>%
    gt::tab_options(
      table.font.names = "Times New Roman",
          table.font.size = 10,
          quarto.use_bootstrap = FALSE,
          quarto.disable_processing = TRUE,
          data_row.padding = px(1),
          summary_row.padding = gt::px(1),
          grand_summary_row.padding = gt::px(1),
          row_group.padding = gt::px(1)
    ) %>%
  tab_style(style = cell_text(align = "left"), locations = cells_source_notes()) %>%
  tab_style(style = cell_text(align = "left"), locations = cells_footnotes())

# save tbl as image
gt::gtsave(tbl_a, file = file.path(here::here("_tables/tbl-time-working-on-module-pairwise-comparisons.pdf")))
gt::gtsave(tbl_a, file = file.path(here::here("_tables/tbl-time-working-on-module-pairwise-comparisons.docx")))
gt::gtsave(tbl_a, file = file.path(here::here("_tables/tbl-time-working-on-module-pairwise-comparisons.png")))

tbl <- tbl %>%
    as_kable_extra(
        booktabs = TRUE,
        linesep = ""
    ) %>%
    kable_styling(
        latex_options = c("scale_down", "hold_position"),
        full_width = TRUE,
        font_size = 8
    )

tbl
```
